---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# quickmap

<!-- badges: start -->
<!-- badges: end -->

**quickmap** is a package for previewing spatial data as interactive
leaflet maps in R. It distinquishes itself from other similar R packages by
beeing able to automatically coerce a wide variety of inputs to leaflet maps



## Installation


And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("s-fleck/quickmap")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval = FALSE}
library(quickmap)

# coordinate pairs without names are interpreted as longitude/latitude
quickmap::qmap(c(16.422524, 48.185686))

# quickmap tries its best to guess the correct order from names
quickmap::qmap(c(LAT = 48.185686, LoNgItuDE = 16.422524))

```

